---
title: "Lab 10"
author: ""
date: ""
output: 
  html_document:
    toc: true
    number_sections: false
    toc_float: true
    df_print: paged
---

```{r setup, include=FALSE}
db <- DBI::dbConnect(RSQLite::SQLite(), dbname = "db/vet.sqlite")
knitr::opts_chunk$set(echo = FALSE, comment = NA, message = FALSE, 
                      warning = FALSE, connection = "db")
```

## Introduction

In your repository you will find a directory named `data/` that contains four
CSV files with information on pet owners, their pets, and their pets' procedure
details and history. These CSV files have been added to the sqlite database
`db/vet.sqlite`. Use the database and CSV files to complete the following tasks.

## Packages

```{r}
library(tidyverse)
library(RSQLite)
library(DBI)
```

## Tasks

Tasks 2 - 6 should use SQL code chunks along with SQL commands to 
complete the task. Rename necessary fields so there is a consistent naming 
scheme in your final table outputs.

The `setup` chunk already has the code to connect to the database.

#### Task 1

In an R chunk, list all tables and their fields that exist in 
`vet.sqlite`.

#### Task 2

Use `COUNT(*)` to determine how many total records exist in `procedure_history`.

#### Task 3

Get a table of owners that live in one of "Grand Rapids", "Kalamazoo", or
"Traverse City".

#### Task 4

Which owners have a single pet that is a dog? Only output a table with each 
owner's name and surname, and the type of pet and the pet's name. *Hint*:
the `HAVING` clause can have aggregate functions in it.

#### Task 5

Which pet under the age of 10 had the most procedures according to the
procedure history? Only return a table with the pet's name, kind, age, and 
number of procedures.

#### Task 6

Get a table that contains the owner id, owner name, owner surname, owner city,
and the total price they spent on procedures corresponding to procedure sub
code 05. Only consider those owners from Lansing, Detroit, and Grand Rapids.
Sort your table in ascending order by city and descending order by the total
price within each city.

#### Task 7

Use the necessary CSV files in `data/` to redo Task 4 using only `dplyr` 
functions in an R code chunk. Check out `?left_join()` for help on R's
join functions.

#### Task 8

Construct an SQL query that outputs a table you can then use to create a 
single visualization with `ggplot2`. Use SQL chunk option 
`output.var="name_of_R_object"`, where in quotes you can specify the name of 
the resulting table and use that name as a reference in R code chunks.